Equalizer\\Programming and User Guide

### 2011-02-11 Developer/ProgrammingGuide/paper.tex
Minor cleanup
[ ] May break build
[ ] May break existing applications (see CHANGES.txt)
[ ] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[ ] Documentation

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya, Jonas B\"osch, Christian
Marten, Sarah Amsellem, Patrick Bouchaud, Philippe Robert and Robert Hauck.

@@

\fig{fViewLoadBalancing}\footnote{Image Copyright Realtime Technology
  AG, 2008} illustrates this process. On the left side, a static
assignment of resources to display segments is used. The right-hand
segment has a higher load than the left-hand segment, causing
sub-optimal performance. The configuration on the left uses a view
equalizer, which assigns two GPU's to the left segment and four GPU's to
the right segment, which leads to optimal performance for this model and
camera position.

>>>>

Written by Stefan Eilemann.\\ Contributions by Maxim Makhinya, Jonas B\"osch,
Christian Marten, Sarah Amsellem, Patrick Bouchaud, Philippe Robert, Robert
Hauck and Lucas Peetz Dulley.

@@

\fig{fViewLoadBalancing}\footnote{Image Copyright Realtime Technology
  AG, 2008} illustrates this process. On the left side, a static
assignment of resources to display segments is used. The right-hand
segment has a higher load than the left-hand segment, causing
sub-optimal performance. The configuration on the right uses a view
equalizer, which assigns two GPU's to the left segment and four GPU's to
the right segment, which leads to optimal performance for this model and
camera position.
